title

### 2013-02-04 paper.tex
Added stuff

To do this, we implement a variant of a minimum spannning tree algorithm
on the complete graph of counties with edges weighted by distance:

(add a flowchart here)

>>>>

To do this, we implement Kruskal's minimum spannning tree algorithm
on the complete graph of counties with edges weighted by distance.

From GPS coordinates of the (geographical) centroids of all 3109 mainland counties, we calculated the adjacency matrix $d[i,j]$ of all county pairs, weighted by geographical distance.

Running Kruskal's algorithm with a priority queue and a union-find data structure we were able to calculate the full minimal spanning tree in under a minute of running time.
